---
title: "Resilience Survey Overview"
author: 
- "Valentyn Hatsko"
- "Andriy Koval"  
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

> This report visualizes key information about Resilience Survey

***Important Definitions***

> Research Sample: Hromadas who responded to the survey.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->

```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

```{r set_options, echo=F, message=FALSE, warning=FALSE, results = 'hide'}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/survey-overview/survey-overview-hatsko.R") #This allows knitr to call chunks tagged in the underlying *.R file.
Sys.setlocale("LC_CTYPE", "ukr")
```

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

<details>

<summary>Packages used </summary>

Packages used in current report

```{r load-packages, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>External scripts </summary>

Collection of custom functions used in current repository (`sda-information-requests`)

```{r load-sources, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Global values </summary>

Values used throughout the report.

```{r declare-globals, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Functions </summary>

Custom functions defined for use in this report.

```{r declare-functions, message=message_chunks, echo=T, results="hide"}
```

</details>

# Data

## Input

```{r load-data, results='show', message=FALSE, cache = T, echo=F, eval=T}
```

<details>

<summary>click to glimpse </summary>

```{r inspect-data, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

Next, we define useful sets of variable names to be used throughout the report

<details>

<summary>click to see the groups </summary>

```{r variable-groups, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

<details>

<summary>meta data </summary>

```{r meta-data-1,  class.source = "fold-show"}
```

</details>

## Transformations

For the state `ds0`, we augment the focal table of the report with additional columns and transform existing variable to better fit visualization/modeling needs

```{r tweak-data-0, results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
```

To make our analysis more nimble we create four alternative versions of `ds1` with Invasion Preparedness questions

<details>

<summary>show transformations </summary>

```{r tweak-data-1-prep,  class.source = "fold-show"}
```

```{r tweak-data-1-info,  class.source = "fold-show"}
```


</details>

<details>

<summary>examine the versions </summary>

```{r inspect-data-1,  class.source = "fold-show"}
```

</details>

# Variable List

The following variables are present in the processed data table of survey responses:

```{r results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
ds0 %>% explore::describe_all() %>%neat_DT()
```

# 0. Introduction

<mark>0.1</mark> What is the goal of this report?

> This report overviews the responses to the survey conducted by KSE Institute in Ukraine during 2022


# 1. General Information

```{r results="show", class.source = "fold-hide"}
meta_survey %>% filter(group=="preamble") %>% pull(label) %>% cat()
```

<mark>1.1</mark> How many hromadas contributed responses to so far?

> As of `r Sys.Date() %>% as.character()`, `r ds0 %>% summarize(response_count = n_distinct(hromada_code)) %>% pull(response_count) %>% scales::comma()` hromadas contributed valid response to the survey

<mark>1.2</mark> What oblasts are represented in this sample? 


```{r class.source="fold-hide"}
ds_survey %>% 
  group_by(region_en, oblast_name_en) %>% 
  summarize(
    hromada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  right_join(
    ds_general %>% 
      group_by(region_en, oblast_name_en) %>% 
      summarize(hromada_count_total = n())
  ) %>% 
  filter(!is.na(region_en)) %>%
  mutate(
    hromada_count = replace_na(hromada_count, 0)
    ,prop = hromada_count/hromada_count_total
    ,pct = scales::percent(prop, accuracy = .1)
  ) %>% 
  arrange(region_en, desc(prop)) %>% 
  select(-prop) %>% 
  ungroup() %>%
  # neat_DT()
  gt::gt() %>%
  gt::cols_label(region_en = 'Region',
                 oblast_name_en = 'Oblast',
                 hromada_count_total = 'Total number \nof ATCs',
                 hromada_count = 'ATCs in the survey',
                 pct = 'Survey Coverage of ATCs'
  )

```



<mark>1.3</mark> What type of hromadas are represented in the sample? 


```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("type"))+
  labs(
    title = "What types of hromadas repsonded to the survey?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )
```

<mark>1.4</mark> What hromadas experienced military occupation or  military actions? 
```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("military_action"))+
  labs(
    title = "How many respondent hromadas have experienced military action at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )

(ds0 %>% make_bi_freq_graph("occupation"))+
  labs(
    title = "How many respondent hromadas have experienced occupation at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y=NULL
  )
ds0 %>% make_bi_freq_graph("military_action","occupation")
ds0 %>% make_bi_freq_graph("occupation","military_action")

```



# 2. Preparation



```{r preparation-summary-1, fig.height=5, fig.width=12,class.source="fold-hide", cache=T}
d_meta_prep <- 
  meta_survey %>% 
  filter(group=="preparation") %>% 
  select(item_name = name,label_en,label)

d1 <- 
  ds1_prep_ordinal_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_prep_binary_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(value == "Yes")
  ) %>% 
  left_join(
    d_meta_prep
  ) %>% 
  arrange(item_name, value) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_prep) %>%
        filter(value == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,value = fct_relevel(
      value
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) 

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(value !="Yes") %>% mutate(value=factor(value))
    ,aes(x=prop, y = display_name, fill=value)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(value !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(value=="Yes") %>% mutate(value=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "Have your hromada made the following preparations?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
# g %>% quick_save("2-preparation-summary-yes",w=12,h=5)
```

<mark>2.1</mark> What questions were asked about preparations hromadas made? 

```{r class.source = "fold-hide"}
ds0 %>% 
  select(preparation) %>% 
  explore::describe_all() %>% 
  left_join(
    meta_survey %>% filter(group=="preparation") %>% select(name,label_en,label)
    ,by=c("variable"="name")) %>% 
  relocate(c("label_en","label"),.after = "variable") %>% 
  select(1:3) %>%
  neat()
```


# 3. Information


```{r results="show", class.source="fold-hide"}
meta_survey %>% filter(group=="information_hat") %>% pull(label) %>% cat()
```

```{r information-summary-1, fig.height=3, fig.width=12,class.source="fold-hide"}

d1 <- 
  ds1_info %>% 
  pivot_longer(
    cols = item_information
    ,names_to = "item_name"
    ,values_to = "item_response"
  ) %>% 
  group_by(item_name,item_response) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_info %>% 
   pivot_longer(
    cols = item_information
    ,names_to = "item_name"
    ,values_to = "item_response"
  ) %>% 
  mutate(
    item_response = case_when(
      item_response != "No" ~ "Yes"
    )
  ) %>%
  group_by(item_name,item_response) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(item_response == "Yes")
  ) %>% 
  left_join(
    d_meta_info
  ) %>% 
  arrange(item_name, item_response) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_info) %>%
        filter(item_response == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,item_response = fct_relevel(
      item_response
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) 

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(item_response !="Yes") %>% mutate(item_response=factor(item_response))
    ,aes(x=prop, y = display_name, fill=item_response)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(item_response !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(item_response=="Yes") %>% mutate(item_response=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "What channels of communication are used to dissiminate information?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}

d <- 
  ds0 %>%  
  select(hromada_code,head_hromada_communication, facebook,viber,telegram ) %>% 
  pivot_longer(cols = c("facebook","viber","telegram")) %>% 
  mutate(
    had_sn_before = case_when(
      value %in% c(0,1) ~ "No cccount before Feb24"
      ,value %in% c(2)  ~ "Had cccount before Feb24"
    )
  ) %>% 
  arrange(hromada_code, head_hromada_communication) %>% 
  group_by(hromada_code,head_hromada_communication) %>% 
  mutate(
    had_any_sn_before_feb24 = sum(value==2,na.rm = T)>0
  ) %>% 
  ungroup() %>% 
  distinct(hromada_code, head_hromada_communication,had_any_sn_before_feb24) %>% 
  mutate(
    time_per_week = fct_recode(head_hromada_communication,
        "1"  = "once_a_week"    
      , "7"  = "once_a_day"   
      , "0"  = "none"   
      , "3"  = "few_times_a_week"  
      , "15" = "2_3_times"   
    ) %>% as.character() %>% as.integer()
    , head_hromada_communication = fct_recode(
      head_hromada_communication,
       "Once a week"      = "once_a_week"
      ,"Once a day"       = "once_a_day"
      ,"Never"            = "none"
      ,"Few times a week" = "few_times_a_week"
      ,"2-3 times a day"  = "2_3_times"
    ) %>% factor( levels = c(
       "Never"           
       ,"Once a week"     
       ,"Few times a week"
       ,"Once a day"      
       ,"2-3 times a day"
    )
    )
  ) 
(d %>% make_bi_freq_graph("had_any_sn_before_feb24")) +
  labs(
    title = "Did hromadas have account on any social network before the invasion?"
    ,subtitle = "Social networks considered: Facebook, Viber, Telegram"
    ,y = NULL, x = NULL, fill = "Had account"
  ) +
  scale_x_discrete(labels=c('TRUE' = 'Had account', 'FALSE' = 'No account')) +
  scale_fill_discrete(labels=c('TRUE' = 'Had account', 'FALSE' = 'No account'))
```


```{r results="show", class.source="fold-hide"}
meta_survey %>% filter(group=="information_freq") %>% pull(label) %>% cat()
```


```{r info-1 , fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% 
  mutate(
    
    head_hromada_communication = fct_recode(
      head_hromada_communication,
       "Once a week"      = "once_a_week"
      ,"Once a day"       = "once_a_day"
      ,"Never"            = "none"
      ,"Few times a week" = "few_times_a_week"
      ,"2-3 times a day"  = "2_3_times"
    ) %>% factor( levels = c(
       "Never"           
       ,"Once a week"     
       ,"Few times a week"
       ,"Once a day"      
       ,"2-3 times a day"
    )
    )
  ) %>% 
  make_bi_freq_graph("head_hromada_communication") )+
  labs(
    title = "How frequently did hromada head communicated in the first month of invasion?"
    ,x = NULL, fill = NULL
  )

```

```{r info-3 , fig.height=3, fig.width=9,class.source="fold-hide"}

d %>% 
  group_by(had_any_sn_before_feb24) %>% 
  summarize(mean_times_per_week = mean(time_per_week,na.rm =T)) %>% 
  ggplot(aes(x=mean_times_per_week, y= had_any_sn_before_feb24,
             fill = had_any_sn_before_feb24))+
  geom_col()+
  geom_text(aes(label=scales::comma(mean_times_per_week)))+
  labs(
    title = "How frequently did heads of hromadas communicate with the community during the first month of invation \ndepending on having any social account before 24th February?"
    ,subtitle = "Social networks considered: Facebook, Viber, Telegram"
    ,y = NULL, x = "Average times per week", fill = "Had account on\nany social network"
  ) +
  scale_y_discrete(labels=c('TRUE' = 'Had account', 'FALSE' = 'No account')) +
  scale_fill_discrete(labels=c('TRUE' = 'Had account', 'FALSE' = 'No account'))

```

```{r info-4 , fig.height=3, fig.width=9,class.source="fold-hide"}

d %>% 
  group_by(head_hromada_communication,had_any_sn_before_feb24) %>% 
  summarize(
    hromada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(had_any_sn_before_feb24) %>% 
  mutate(
    prop = hromada_count/sum(hromada_count)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ggplot(aes(x=prop, y = head_hromada_communication, fill = had_any_sn_before_feb24))+
  geom_col(position = position_dodge())+
  geom_text(aes(label = pct), hjust = -.5,position = position_dodge(width = .9))+
  scale_x_continuous(labels = scales::percent_format(),expand = expansion(add = c(0,.1)))+
  ggplot2::scale_fill_viridis_d(begin = 0, end = .8, direction = -1, option = "plasma",guide= guide_legend(reverse=T)
                                ,labels = c('TRUE' = 'Had account', 'FALSE' = 'No account')
    )+
  labs(
    title = "How frequently did heads of hromadas communicated during the first month of invasion?"
    ,fill = "Had accounts\non social networks\nbefore Feb 24"
    ,x = "Percent of respondents in each group"
    , y = NULL
  )
```


# 4. National Resistance

```{r results="show", class.source="fold-hide"}
meta_survey %>% filter(name=="dftg_creation") %>% pull(label) %>% cat()

```

```{r dftg-1, fig.height=3, fig.width=9,class.source="fold-hide"}

d <- ds0 %>% 
  select(hromada_code, dftg_creation, type) %>%
  mutate(dftg_creation = factor(dftg_creation, levels = c('not_able', 'still_not', 'yes')),
         type = factor(type, levels = c('сільська', "селищна", "міська")),
         dftg_creation = fct_recode(dftg_creation,
             'Yes' = 'yes'
            ,"Didn't due to quick occupation" = 'not_able'
            ,'Still not created' = 'still_not')
  )

(d %>% make_bi_freq_graph('dftg_creation')) +
  labs(
    title = "Did hromadas create a voluntary formation of a territorial community?"
    ,y = NULL, x = NULL, fill = NULL
  )
```

Many village communities didn't have a voluntary formation of a territorial community at the time of the survey

```{r dftg-2, fig.height=3, fig.width=9,class.source="fold-hide"}
d %>%
  group_by(type) %>%
  count(dftg_creation) %>%
  mutate(prop = n/sum(n)
         ,pct = scales::percent(prop, accuracy = 1)) %>% 
  ggplot(aes(x=prop, y = dftg_creation, fill = type))+
  geom_col(position = position_dodge())+
  geom_text(aes(label = pct), hjust = -.5,position = position_dodge(width = .9))+
  scale_x_continuous(labels = scales::percent_format(),expand = expansion(add = c(0,.1)))+
  ggplot2::scale_fill_viridis_d(begin = 0, end = .8, direction = -1, option = "plasma",guide= guide_legend(reverse=T)
  )+
  labs(
    title = "Did hromadas create a voluntary formation of a territorial community?"
    ,fill = "Hromada Type"
    ,x = "Percent of respondents in each group"
    , y = NULL
  )
```

```{r dftg-date, fig.height=5, fig.width=9,class.source="fold-hide"}
d <- ds0 %>% select(dftg_creation_date) %>% group_by(dftg_creation_date) %>% 
  summarise(n = n()) %>%
  filter(!is.na(dftg_creation_date) & dftg_creation_date > '2021-12-28') %>%
  mutate(cum = cumsum(n))

p <- d %>%
  ggplot(aes(x = dftg_creation_date, y = cum)) +
  geom_point() +
  geom_vline(aes(xintercept = as.POSIXct('2022-02-24')), 
             color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept = as.POSIXct('2021-12-29')), 
             color = 'red', linetype = 'dashed') +
  geom_rect(aes(xmin = as.POSIXct('2022-02-24'), xmax = as.POSIXct('2022-03-24'), 
                ymin = -Inf, ymax = Inf),
            color = 'coral1', fill = 'coral1', alpha = 0.02) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_x_datetime(limits = c(as.POSIXct('2021-12-01'), as.POSIXct('2022-10-15')), date_breaks = '1 month') +
  annotate(geom = 'label', x = as.POSIXct('2021-12-31'), y = 80, size = 3,
           label = 'December 29th: \nThe order of formation and \nactivity of the voluntary \nformations of ATC was defined') +
  annotate(geom = 'label', x = as.POSIXct('2022-02-28'), y = 70, size = 3,
           label = 'Full-scale \nrussian invasion') +
  annotate(geom = 'text', x = as.POSIXct('2022-03-26'), y = 90, hjust = 0, size = 3,
           label = '59 voluntary formations of ATC \nafter a first month', fontface = 'italic') +
  labs(title = 'Number of DFTG created by ATCs')
p

```

```{r dftg-date-1, fig.height=5, fig.width=9,class.source="fold-hide"}
d <- ds0 %>% select(dftg_creation_date, type) %>% group_by(dftg_creation_date, type) %>% 
  filter(!is.na(dftg_creation_date) & dftg_creation_date > '2021-12-28') %>%
  summarise(n = n()) %>%
  pivot_wider(values_from = n, names_from = type) %>%
  rename(c = 'міська', v = 'сільська', s = 'селищна') %>%
  ungroup() %>% 
  mutate(c = replace_na(c, 0),
         v = replace_na(v, 0),
         s = replace_na(s, 0),
         c_cum = cumsum(c),
         s_cum = cumsum(s),
         v_cum = cumsum(v)) %>% 
  select(-c(c,v,s)) %>%
  pivot_longer(-dftg_creation_date, values_to = 'n', names_to = 'type')

p <- d %>%
  ggplot(aes(x = dftg_creation_date, y = n, color = type)) +
  geom_point() +
  geom_vline(aes(xintercept = as.POSIXct('2022-02-24')), 
             color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept = as.POSIXct('2021-12-29')), 
             color = 'red', linetype = 'dashed') +
  geom_rect(aes(xmin = as.POSIXct('2022-02-24'), xmax = as.POSIXct('2022-03-24'), 
                ymin = -Inf, ymax = Inf),
            color = 'coral1', fill = 'coral1', alpha = 0.007) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = 'top') +
  scale_x_datetime(limits = c(as.POSIXct('2021-12-01'), as.POSIXct('2022-10-15')), date_breaks = '1 month') +
  scale_y_continuous(limits = c(0,40)) +
  scale_color_discrete(labels = c('c_cum' = 'City', 's_cum' = 'Urban Village', 'v_cum' = 'Village')) +
  annotate(geom = 'label', x = as.POSIXct('2021-12-31'), y = 36, size = 3,
           label = 'December 29th: \nThe order of formation and \nactivity of the voluntary \nformations of ATC was defined') +
  annotate(geom = 'label', x = as.POSIXct('2022-02-28'), y = 37, size = 3,
           label = 'Full-scale \nrussian invasion') +
  annotate(geom = 'text', x = as.POSIXct('2022-03-26'), y = 37, hjust = 0, size = 3,
           label = '59 voluntary formations of ATC \nafter a first month', fontface = 'italic') +
  labs(title = 'Number of DFTG created by ATCs', color = NULL)
p

```

## 4.1 Transport Help

# 5. Administrative Adaptation

# 6. Evacuation

# 7. IDP

# 8. Economics

# 9. Humanitarian

# 10. Reconstructioin

## 10.1 Demage Evaluation

# 11. Current Challenges

## 11.1 Heating season

## 11.2 Problem Involvement

```{r}
meta_survey %>% filter(group=="preparation") %>% pull(name)


```

# Session Information {#session-info}

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Environment </summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
    } else {
      sessionInfo()
    }
```

</details>

```{r session-duration, echo=FALSE}
    report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
