---
title: "Resilience Survey Overview"
author: 
- "Valentyn Hatsko"
- "Andriy Koval"  
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

> This report visualizes key information about Resilience Survey

***Important Definitions***

> Research Sample: Hromadas who responded to the survey.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->

```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

```{r set_options, echo=F, message=FALSE, warning=FALSE, results = 'hide'}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/survey-overview/survey-overview.R") #This allows knitr to call chunks tagged in the underlying *.R file.
Sys.setlocale("LC_CTYPE", "ukr")
```

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

<details>

<summary>Packages used </summary>

Packages used in current report

```{r load-packages, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>External scripts </summary>

Collection of custom functions used in current repository (`sda-information-requests`)

```{r load-sources, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Global values </summary>

Values used throughout the report.

```{r declare-globals, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Functions </summary>

Custom functions defined for use in this report.

```{r declare-functions, message=message_chunks, echo=T, results="hide"}
```

</details>

# Data

## Input

```{r load-data, results='show', message=FALSE, cache = F, eval=T}
```

<details>

<summary>click to glimpse </summary>

```{r inspect-data, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

Next, we define useful sets of variable names to be used throughout the report

<details>

<summary>click to see the groups </summary>

```{r variable-groups, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

<details>

<summary>meta data </summary>

```{r meta-data-1,  class.source = "fold-show"}
```

</details>

## Transformations

For the state `ds0`, we augment the focal table of the report with additional columns and transform existing variable to better fit visualization/modeling needs

```{r tweak-data-0, results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
```

To make our analysis more nimble we create four alternative versions of `ds1` with Invasion Preparedness questions

<details>

<summary>show transformations </summary>

```{r tweak-data-1-prep,  class.source = "fold-show"}
```

```{r tweak-data-1-info,  class.source = "fold-show"}
```


</details>

<details>

<summary>examine the versions </summary>

```{r inspect-data-1,  class.source = "fold-show"}
```

</details>

# Variable List

The following variables are present in the processed data table of survey responses:

```{r results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
ds0 %>% explore::describe_all() %>%neat_DT()
```

# 0. Introduction

<mark>0.1</mark> What is the goal of this report?

> This report overviews the responses to the survey conducted by \_\_\_\_\_ in Ukraine during 2022


# 1. General Information

```{r results="show"}
meta_survey %>% filter(group=="preamble") %>% pull(label) %>% cat()
```

<mark>1.1</mark> How many hromadas contributed responses to so far?

> As of `r Sys.Date() %>% as.character()`, `r ds0 %>% summarize(response_count = n_distinct(hromada_code)) %>% pull(response_count) %>% scales::comma()` hromadas contributed valid response to the survey

<mark>1.2</mark> What oblasts are represented in this sample>? 


```{r class.source="fold-hide"}
ds_survey %>% 
  group_by(region_en, oblast_name_en) %>% 
  summarize(
    hormada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  left_join(
    ds_general %>% 
      group_by(region_en=region_en.y,  oblast_name_en=oblast_name_en.x ) %>% 
      summarize(hromada_count_total = n())
  ) %>% 
  mutate(
    prop = hormada_count/hromada_count_total
    ,pct = scales::percent(prop, accuracy = .1)
  ) %>% 
  arrange(region_en, oblast_name_en) %>% 
  select(-prop) %>% 
  ungroup() %>%
  # neat_DT()
  neat()
```



<mark>1.3</mark> What type of hromadas are represented in the sample? 


```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("type"))+
  labs(
    title = "What types of hromadas repsonded to the survey?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )
```

<mark>1.4</mark> What hromadas experienced military occupation or  military actions? 
```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("military_action"))+
  labs(
    title = "How many respondent hromadas have experienced military action at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )

(ds0 %>% make_bi_freq_graph("occupation"))+
  labs(
    title = "How many respondent hromadas have experienced occupation at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y=NULL
  )
ds0 %>% make_bi_freq_graph("military_action","occupation")
ds0 %>% make_bi_freq_graph("occupation","military_action")

```



# 2. Preparation



```{r preparation-summary-1, fig.height=5, fig.width=12,class.source="fold-hide", cache=T}


d1 <- 
  ds1_prep_ordinal_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_prep_binary_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(value == "Yes")
  ) %>% 
  left_join(
    d_meta_prep
  ) %>% 
  arrange(item_name, value) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_prep) %>%
        filter(value == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,value = fct_relevel(
      value
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) 

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(value !="Yes") %>% mutate(value=factor(value))
    ,aes(x=prop, y = display_name, fill=value)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(value !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(value=="Yes") %>% mutate(value=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "Have your hromada made the following preparations?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
# g %>% quick_save("2-preparation-summary-yes",w=12,h=5)
```

<mark>2.1</mark> What questions were asked about preparations hromadas made? 

```{r class.source = "fold-hide"}
ds0 %>% 
  select(preparation) %>% 
  explore::describe_all() %>% 
  left_join(
    meta_survey %>% filter(group=="preparation") %>% select(name,label_en,label)
    ,by=c("variable"="name")) %>% 
  relocate(c("label_en","label"),.after = "variable") %>% 
  select(1:3) %>%
  neat()
```

## Item-total correlation 

We can conceptualize the preparation for invation as two scores: the first received for steps taken prior to Feb 24, 2022 (the `Before` prep score) and the second for the steps undertaken after Feb 24 (the `After` prep score), as recorded at the time of data collection ( October - November 20200). 


```{r}
ds1_prep %>% select(1:4) # + individual preparation items
# prep_score =  0 to  30, sum of (0|1|2) for each of 15 items, 2 pts for prepping before 2022-02-24 1 pts after.
# prep_score_before = 0 to 15, sum of (0|1) items, where 1 = prepping before Feb 24
# prep_score_after = 0 to 15, sum of (0|1) items, where 1 = prepping eventually (Nov 2022)

```

 These  scores have a convenient conceptualization and a straightforward interpretation
 
 - `Before` - number of preparatory items on the prep list completed before Feb 24
 - `AFter` - number of preparatory steps completed by the hromada at the time of the interview
 - `Total` - the sum of `Before` and `After`. Evaluates the readiness of the hromada at the time of the interview, valuing steps undertaken prior to Feb 24 twice as influential in the final score

`Before` and `After` scores have a more clear conceptualization, but th `Total` score has a more appealing distribution shape, making it more useful for statistical modeling. 

```{r info-score-distribution, fig.height=6, fig.width=4,class.source="fold-hide", cache=T}

g <-  ds1_prep %>%
  # To standardize the metrics of each scale : 0 to 10, where 10 - most prepared
  mutate(
     prep_score = prep_score / 3 # because 15 items, maximum 2 points each
    ,prep_score_before =prep_score_before /1.5 # because 15 items, maximum 1 point each
    ,prep_score_after = prep_score_after /1.5 # because 15 items, maximum 1 point each
  ) %>% 
  select(starts_with("prep_score")) %>% 
  pivot_longer(cols = everything(),names_to = "measure",values_to="value") %>% 
  mutate( 
    measure = factor(measure,
                        levels = c("prep_score_before","prep_score_after","prep_score")
                        ,labels = c("Prep Score (Before)","Prep Score (After)", "Prep Score")
                        )
  ) %>% 
  ggplot(aes(x=value))+
  geom_histogram(binwidth = 1, alpha = .4)+
  scale_x_continuous(breaks = seq(0,10,1))+
  facet_wrap("measure",ncol =1)
g
g %>%  quick_save("score-distribution",w=4, h=6)
```

The item-total correlation also indicates that psychometrically the `Total` score is a better choice - having no negative values and generally having a higher discrimination capacity of items.   

```{r prep-item-total, fig.height=4, fig.width=8,class.source="fold-hide", cache=T}
(d_item_total%>% 
  slice(1:15) %>% 
  pivot_longer(
     cols = c("Total","Before","After")
    ,names_to = "scenario"
    ,values_to = "correlation"
  ) %>% 
  mutate(
    discrimination = case_when(
      correlation <= 0  ~ "problematic"
      ,correlation > 0 & correlation < .2 ~ "poor"
      ,correlation >=.2 & correlation < .4 ~ "good"
      ,correlation >=.4  ~ "very good"
    ) %>% factor(levels = c("problematic","poor","good","very good"))
    ,scenario = scenario %>% factor(level=c("Before","After","Total"))
    ,item_name = factor(item_name, levels = d_meta_prep %>% pull(label_en)) %>% 
      fct_rev()
  ) %>% 
  ggplot(aes(x = item_name, y = correlation, color = discrimination, group = scenario))+
  geom_line(aes(group = "scenario"))+
  geom_point()+
  geom_text(aes(label=correlation %>% scales::number(accuracy = .01) %>% RemoveLeadingZero()),hjust=-.3
            ,size = 3)+
  geom_hline(aes(x=0, yintercept = 0))+ 
  facet_wrap("scenario",nrow=1)+
  scale_y_continuous(limits = c(-.3,.6), expand = expansion(add = c(0,.2)))+
  scale_color_brewer(type ="div",palette = "RdYlGn")+
  coord_flip() +
    labs(
      title = "Item-total corellations under three measurement scenarios"
      ,subtitle = "Before = prior to Feb 24, After = at time of interview, Oct-Nov 2022, Total = Before + After"
      ,y = "Item-total Correlation (Spearman)"
      ,x = NULL
      ,color = "Discrimination"
    )
  ) %>% 
  print() %>% 
  quick_save("item-total",w=8,h=4)
```

While all three metrics should be considered during modeling, our current understanding of the data sugggests that we should prefer the `Total` score in relating hromada's preparedness to other attributes. 


# 3. Information


```{r results="show", calss.source="fold-hide"}
meta_survey %>% filter(group=="information_hat") %>% pull(label) %>% cat()
```

```{r information-summary-1, fig.height=3, fig.width=12,class.source="fold-hide"}

d1 <- 
  ds1_info %>% 
  pivot_longer(
    cols = item_information
    ,names_to = "item_name"
    ,values_to = "item_response"
  ) %>% 
  group_by(item_name,item_response) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_info %>% 
   pivot_longer(
    cols = item_information
    ,names_to = "item_name"
    ,values_to = "item_response"
  ) %>% 
  mutate(
    item_response = case_when(
      item_response != "No" ~ "Yes"
    )
  ) %>%
  group_by(item_name,item_response) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(item_response == "Yes")
  ) %>% 
  left_join(
    d_meta_info
  ) %>% 
  arrange(item_name, item_response) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_info) %>%
        filter(item_response == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,item_response = fct_relevel(
      item_response
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) 

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(item_response !="Yes") %>% mutate(item_response=factor(item_response))
    ,aes(x=prop, y = display_name, fill=item_response)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(item_response !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(item_response=="Yes") %>% mutate(item_response=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "What channels of communication are used to dissiminate information?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
```


```{r results="show", calss.source="fold-hide"}
meta_survey %>% filter(group=="information_freq") %>% pull(label) %>% cat()
```


```{r info-1 , fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% 
  mutate(
    
    head_hromada_communication = fct_recode(
      head_hromada_communication,
       "Once a week"      = "once_a_week"
      ,"Once a day"       = "once_a_day"
      ,"Never"            = "none"
      ,"Few times a week" = "few_times_a_week"
      ,"2-3 times a day"  = "2_3_times"
    ) %>% factor( levels = c(
       "Never"           
       ,"Once a week"     
       ,"Few times a week"
       ,"Once a day"      
       ,"2-3 times a day"
    )
    )
  ) %>% 
  make_bi_freq_graph("head_hromada_communication") )+
  labs(
    title = "How frequently did hromada head communicated in the frist month of invasion?"
    ,x = NULL
  )

```


```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}

d <- 
  ds0 %>%  
  select(hromada_code,head_hromada_communication, facebook,viber,telegram ) %>% 
  pivot_longer(cols = c("facebook","viber","telegram")) %>% 
  mutate(
    had_sn_before = case_when(
      value %in% c(0,1) ~ "No cccount before Feb24"
      ,value %in% c(2)  ~ "Had cccount before Feb24"
    )
  ) %>% 
  arrange(hromada_code, head_hromada_communication) %>% 
  group_by(hromada_code,head_hromada_communication) %>% 
  mutate(
    had_any_sn_before_feb24 = sum(value==2,na.rm = T)>0
  ) %>% 
  ungroup() %>% 
  distinct(hromada_code, head_hromada_communication,had_any_sn_before_feb24) %>% 
  mutate(
    time_per_week = fct_recode(head_hromada_communication,
        "1"  = "once_a_week"    
      , "7"  = "once_a_day"   
      , "0"  = "none"   
      , "3"  = "few_times_a_week"  
      , "15" = "2_3_times"   
    ) %>% as.character() %>% as.integer()
    , head_hromada_communication = fct_recode(
      head_hromada_communication,
       "Once a week"      = "once_a_week"
      ,"Once a day"       = "once_a_day"
      ,"Never"            = "none"
      ,"Few times a week" = "few_times_a_week"
      ,"2-3 times a day"  = "2_3_times"
    ) %>% factor( levels = c(
       "Never"           
       ,"Once a week"     
       ,"Few times a week"
       ,"Once a day"      
       ,"2-3 times a day"
    )
    )
  ) 
(d %>% make_bi_freq_graph("had_any_sn_before_feb24")) +
  labs(
    title = "Did hromadas have account on any social network?"
    ,subtitle = "Social networks considered: Facebook, Viber, Telegram"
    ,y = NULL, fill = "Had account"
  )
```

```{r info-3 , fig.height=3, fig.width=9,class.source="fold-hide"}

d %>% 
  group_by(had_any_sn_before_feb24) %>% 
  summarize(mean_times_per_week = mean(time_per_week,na.rm =T)) %>% 
  ggplot(aes(x=mean_times_per_week, y= had_any_sn_before_feb24,
             fill = had_any_sn_before_feb24))+
  geom_col()+
  geom_text(aes(label=scales::comma(mean_times_per_week)))+
  labs(
    title = "How freqently did heads of hromadas communicate with the community during the first month of invation?"
    ,subtitle = "Social networks considered: Facebook, Viber, Telegram"
    ,y = NULL, x = "Average times per week", fill = "Had account on\nany social network"
  )

```

```{r info-4 , fig.height=3, fig.width=9,class.source="fold-hide"}

d %>% 
  group_by(head_hromada_communication,had_any_sn_before_feb24) %>% 
  summarize(
    hromada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(had_any_sn_before_feb24) %>% 
  mutate(
    prop = hromada_count/sum(hromada_count)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ggplot(aes(x=prop, y = head_hromada_communication, fill = had_any_sn_before_feb24))+
  geom_col(position = position_dodge())+
  geom_text(aes(label = pct), hjust = -.5,position = position_dodge(width = .9))+
  scale_x_continuous(labels = scales::percent_format(),expand = expansion(add = c(0,.1)))+
  ggplot2::scale_fill_viridis_d(begin = 0, end = .8, direction = -1, option = "plasma",guide= guide_legend(reverse=T)
    )+
  labs(
    title = "How frequently did heads of hromadas communicated during the first month of invation?"
    ,fill = "Had accounts\non social networks\nbefore Feb 24"
    ,x = "Percent of respondents in each group"
    , y = NULL
  )
```


# 4. National Resistance

## 4.1 Transport Help

# 5. Administrative Adaptation

# 6. Evacuation

# 7. IDP

# 8. Economics

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% 
  mutate(
    `Special fund's expenditures were relocated` = fct_recode(
      special_fund_relocation,
       "Yes"      = "yes"
      ,"No"       = "no"
    ) %>% factor( levels = c(
       "Yes"           
       ,"No"     
    )
    )
  ) %>% 
  make_bi_freq_graph("military_action","Special fund's expenditures were relocated") )+
  labs(
    title = "Were budget expenditures from the special fund streamed to finance other, current needs?"
    ,x = NULL
  )
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% filter(military_action=="no_combat") %>%
  mutate(
    `Special fund's expenditures were relocated` = case_when(special_fund_relocation=="no"~0,
                                                             special_fund_relocation=="yes"~1)
  ) %>% 
  ggplot(aes(x = prep_count, y = `Special fund's expenditures were relocated`)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between preparation and special fund realocation for non-combat hromadas') +
  xlab("counted preparations"))
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% filter(military_action=="no_combat") %>%
  mutate(
    `Special fund's expenditures were relocated` = case_when(special_fund_relocation=="no"~0,
                                                             special_fund_relocation=="yes"~1)
  ) %>% 
  ggplot(aes(x = urban_pct, y = `Special fund's expenditures were relocated`)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between urbanisation and special fund realocation for non-combat hromadas') +
  xlab("share of urban population"))
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% filter(military_action=="no_combat") %>%
  mutate(
    `Special fund's expenditures were relocated` = case_when(special_fund_relocation=="no"~0,
                                                             special_fund_relocation=="yes"~1)
  ) %>% 
  ggplot(aes(x = own_income_prop_2021, y = `Special fund's expenditures were relocated`)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between financial autonomy and special fund realocation for non-combat hromadas') +
  xlab("share of own revenue in total budget in 2021"))
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
ds0 %>% 
  filter(special_fund_relocation == "yes") %>% 
  select(hromada_name, `special_fund_relocation_needs/state_functions`:`special_fund_relocation_needs/healthcare`) %>% 
  pivot_longer(-c(hromada_name), names_to = "sector", values_to = "cut") %>% 
  mutate(
    sector = str_to_title(str_remove(sector, "sectors_"))
  ) %>% 
  group_by(sector) %>% 
  summarise(`Number of Hromadas` = sum(cut), .groups = "drop") %>% 
  filter(`Number of Hromadas` > 0)  %>% 
 mutate(sector = case_when(sector=="Special_fund_relocation_needs/Defense"~"Defense",
                           sector=="Special_fund_relocation_needs/Economic_activity"~"Economic Activity",
                           sector=="Special_fund_relocation_needs/Education"~"Education",
                           sector=="Special_fund_relocation_needs/Environment"~"Environment",
                           sector=="Special_fund_relocation_needs/Healthcare"~"Healthcare",
                           sector=="Special_fund_relocation_needs/Social_protection"~"Social Protection",
                           sector=="Special_fund_relocation_needs/Spirit_development"~"Spirit Development",
                           sector=="Special_fund_relocation_needs/State_functions"~"State Functions",
                           sector=="Special_fund_relocation_needs/Utilities"~"Utilities",
                           sector=="Special_fund_relocation_needs/Public_order"~"Public Order",
                           TRUE~sector)
 ) %>%
  ggplot(aes(x = `Number of Hromadas`, y = fct_reorder(sector, `Number of Hromadas`))) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_bw()+
  labs(
    title = "Sectors for which the funds of the special fund were redistributed"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = "Sector"
  )+
  geom_col(position = position_stack()
           , alpha = .5
           ,data =
  )
```

```{r class.source="fold-hide"}
ds0 %>% 
  mutate(relocated_companies = as.numeric(relocated_companies_text)) %>%
      group_by(region_en,  oblast_name_en ) %>% 
      summarize(`Relocated companies` = sum(relocated_companies, na.rm = TRUE)) %>% 
  filter(`Relocated companies`>0) %>%
    ggplot(aes(x = `Relocated companies`, y = fct_reorder(oblast_name_en, `Relocated companies`))) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_bw()+
  labs(
    title = "Relocated businesses by destination region"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = "Oblast"
  )+
  geom_col(position = position_stack()
           , alpha = .5
           ,data =
  )
```

```{r class.source="fold-hide"}
ds0 %>% 
  mutate(relocated_companies = as.numeric(relocated_companies_text)) %>% 
  filter(relocated_companies>0) %>%
    ggplot(aes(y = relocated_companies, x = own_income_prop_2021 )) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between financial autonomy and business relocation inflow') +
  xlab("share of own revenue in total budget in 2021")
  
```

```{r class.source="fold-hide"}
ds0 %>% filter(military_action=="no_combat") %>%
  mutate(relocated_companies = as.numeric(relocated_companies_text)) %>% 
  filter(relocated_companies>0) %>%
    ggplot(aes(y = relocated_companies, x = prep_count )) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between preparations and business relocation inflow')
  
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
(ds0 %>% 
   mutate(
    `Jobs created` = fct_recode(
      created_jobs,
       "Don't know" = "dk",
      "0-50" = "0_50_jobs",
      "51-100" = "51_100_jobs",
      "101-250" = "101_250_jobs"
    ) %>% factor( levels = c(
       "Don't know"           
       ,"0-50" ,
       "51-100",
       "101-250"
    )
    )
  ) %>%
   make_bi_freq_graph("Jobs created"))+
  labs(
    title = "How many jobs were created in the hromada thanks to the relocated enterprises?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )
```

```{r info-2, fig.height=3, fig.width=9,class.source="fold-hide"}
ds0 %>% filter(bussiness_stimules_none == 0) %>%
  select(hromada_name, `bussiness_stimules/tax_benefits`:`bussiness_stimules/other`) %>% 
  pivot_longer(-c(hromada_name), names_to = "type", values_to = "done") %>% 
  mutate(
    type = str_to_title(str_remove(type, "types_"))
  ) %>% 
  group_by(type) %>% 
  summarise(`number of hromadas` = sum(done), .groups = "drop") %>% 
  filter(`number of hromadas`>0) %>% 
  mutate(type = case_when(type == "Bussiness_stimules/Education" ~ "Organized Educational Events",
                          type == "Bussiness_stimules/Free_rooms" ~ "Provided Premises for Free",
                          type == "Bussiness_stimules/Tax_benefits" ~ "Provided with Tax Benefits",
                          type == "Bussiness_stimules/Other" ~ "Other Methods",
  TRUE~type)
  ) %>%
  ggplot(aes(x = `number of hromadas`, y = fct_reorder(type, `number of hromadas`))) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_bw()+
  geom_col(position = position_stack()
           , alpha = .5
           ,data =
  )+
  labs(
    title = "Which incentives have been used to support business in the community since February 24?"
    ,x = "Number of Hromadas", y = NULL, fill = NULL
  )+
  theme(
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
```

# 9. Humanitarian

# 10. Reconstructioin

## 10.1 Demage Evaluation

# 11. Current Challenges

## 11.1 Heating season

## 11.2 Problem Involvement

```{r}
meta_survey %>% filter(group=="preparation") %>% pull(name)


```

# Session Information {#session-info}

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Environment </summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
    } else {
      sessionInfo()
    }
```

</details>

```{r session-duration, echo=FALSE}
    report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
