---
title: "Title"
author: "First Last"  
date: "last Updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: simplex
    highlight: tango
editor_options: 
  chunk_output_type: console
---

This report (add a brief description and the purpose of the report)
Demonstration of the __COMBINED__ template

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F, results = 'hide'}
cat("Working directory: ", getwd()) # turn on to test the location
# if the line above generates the project root, re-map by selecting 
# Session --> Set Working Directory --> To Source File location
```


```{r set_options, echo=F}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
knitr::opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-com/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
```

# Environment
<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. -->
```{r load-packages, message=message_chunks}
# Choose to be greedy: load only what's needed
# Three ways, from least (1) to most(3) greedy:
# -- 1.Attach these packages so their functions don't need to be qualified: http://r-pkgs.had.co.nz/namespace.html#search-path
library(ggplot2)   # graphs
library(forcats)   # factors
library(stringr)   # strings
library(lubridate) # dates
# -- 2.Import only certain functions of a package into the search path.
import::from("magrittr", "%>%")
# -- 3. Verify these packages are available on the machine, but their functions need to be qualified: http://r-pkgs.had.co.nz/namespace.html#search-path
requireNamespace("readr"    )# data import/export
requireNamespace("readxl"   )# data import/export
requireNamespace("tidyr"    )# tidy data
requireNamespace("janitor"  )# tidy data
requireNamespace("dplyr"    )# Avoid attaching dplyr, b/c its function names conflict with a lot of packages (esp base, stats, and plyr).
requireNamespace("testit"   )# For asserting conditions meet expected patterns.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources}
source("../../scripts/common-functions.R")
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals}
```

# Data
```{r load-data, results='show', message=FALSE}

```

```{r tweak-data,echo = echo_chunks, results='show', message=message_chunks}

```

# Analysis

```{r table-1, echo = echo_chunks, results='show', message=message_chunks}

```

```{r graph-1, echo = echo_chunks, results='show', message=message_chunks}

```

```{r graph-2, echo = echo_chunks, results='show', message=message_chunks}

```

Session Information {#session-info}
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
}
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
