---
title: "Modeling Hromada Preparedness"
author: 
- "Andriy Koval"  
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

> This report searches for association between Preparedness Index of hromadas and their 

***Important Definitions***

> Research Sample: Hromadas who responded to the survey.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->

```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

```{r set_options, echo=F, message=FALSE, warning=FALSE, results = 'hide'}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/survey-prep-model/survey-prep-model.R") #This allows knitr to call chunks tagged in the underlying *.R file.
Sys.setlocale("LC_CTYPE", "ukr")
```

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

<details>

<summary>Packages used </summary>

Packages used in current report

```{r load-packages, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>External scripts </summary>

Collection of custom functions used in current repository (`sda-information-requests`)

```{r load-sources, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Global values </summary>

Values used throughout the report.

```{r declare-globals, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>Functions </summary>

Custom functions defined for use in this report.

```{r declare-functions, message=message_chunks, echo=T, results="hide"}
```

</details>

# Data

## Input

```{r load-data, results='show', message=FALSE, cache = F, eval=T}
```

<details>

<summary>click to glimpse </summary>

```{r inspect-data, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

Next, we define useful sets of variable names to be used throughout the report

<details>

<summary>click to see the groups </summary>

```{r variable-groups, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

<details>

<summary>meta data </summary>

```{r meta-data-1,  class.source = "fold-show"}
```

</details>

## Transformations

For the state `ds0`, we augment the focal table of the report with additional columns and transform existing variable to better fit visualization/modeling needs

```{r tweak-data-0, results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
```

To make our analysis more nimble we create four alternative versions of `ds1` with Invasion Preparedness questions

<details>

<summary>show transformations </summary>

```{r tweak-data-1-prep,  class.source = "fold-show"}
```

```{r tweak-data-1-info,  class.source = "fold-show"}
```


</details>

<details>

<summary>examine the versions </summary>

```{r inspect-data-1,  class.source = "fold-show"}
```

</details>

# Variable List

The following variables are present in the processed data table of survey responses:

```{r results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
ds0 %>% explore::describe_all() %>%neat_DT()
```

# 0. Introduction

<mark>0.1</mark> What is the goal of this report?

> This report overviews the responses to the survey conducted by \_\_\_\_\_ in Ukraine during 2022


# 1. General Information

```{r results="show"}
meta_survey %>% filter(group=="preamble") %>% pull(label) %>% cat()
```

<mark>1.1</mark> How many hromadas contributed responses to so far?

> As of `r Sys.Date() %>% as.character()`, `r ds0 %>% summarize(response_count = n_distinct(hromada_code)) %>% pull(response_count) %>% scales::comma()` hromadas contributed valid response to the survey

<mark>1.2</mark> What oblasts are represented in this sample>? 


```{r class.source="fold-hide"}
ds_survey %>% 
  group_by(region_en, oblast_name_en) %>% 
  summarize(
    hormada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  left_join(
    ds_general %>% 
      group_by(region_en,  oblast_name_en) %>% 
      summarize(hromada_count_total = n())
  ) %>% 
  mutate(
    prop = hormada_count/hromada_count_total
    ,pct = scales::percent(prop, accuracy = .1)
  ) %>% 
  arrange(region_en, oblast_name_en) %>% 
  select(-prop) %>% 
  ungroup() %>%
  # neat_DT()
  neat()
```

<mark>1.3</mark> What type of hromadas are represented in the sample? 
```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("type"))+
  labs(
    title = "What types of hromadas repsonded to the survey?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )
```

<mark>1.4</mark> What hromadas experienced military occupation or  military actions? 
```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("military_action"))+
  labs(
    title = "How many respondent hromadas have experienced military action at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )

(ds0 %>% make_bi_freq_graph("occupation"))+
  labs(
    title = "How many respondent hromadas have experienced occupation at the time of the interview?"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y=NULL
  )
ds0 %>% make_bi_freq_graph("military_action","occupation")
ds0 %>% make_bi_freq_graph("occupation","military_action")

```



# 2. Preparation



```{r preparation-summary-1, fig.height=5, fig.width=12,class.source="fold-hide", cache=T}


d1 <- 
  ds1_prep_ordinal_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_prep_binary_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(value == "Yes")
  ) %>% 
  left_join(
    d_meta_prep
  ) %>% 
  arrange(item_name, value) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_prep) %>%
        filter(value == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,value = fct_relevel(
      value
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) 

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(value !="Yes") %>% mutate(value=factor(value))
    ,aes(x=prop, y = display_name, fill=value)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(value !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(value=="Yes") %>% mutate(value=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "Have your hromada made the following preparations?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
# g %>% quick_save("2-preparation-summary-yes",w=12,h=5)
```

<mark>2.1</mark> What questions were asked about preparations hromadas made? 

```{r class.source = "fold-hide"}
ds0 %>% 
  select(preparation) %>% 
  explore::describe_all() %>% 
  left_join(
    meta_survey %>% filter(group=="preparation") %>% select(name,label_en,label)
    ,by=c("variable"="name")) %>% 
  relocate(c("label_en","label"),.after = "variable") %>% 
  select(1:3) %>%
  neat()
```

## Item-total correlation 

We can conceptualize the preparation for invation as two scores: the first received for steps taken prior to Feb 24, 2022 (the `Before` prep score) and the second for the steps undertaken after Feb 24 (the `After` prep score), as recorded at the time of data collection ( October - November 20200). 


```{r}
ds1_prep %>% select(1:4) # + individual preparation items
# prep_score =  0 to  30, sum of (0|1|2) for each of 15 items, 2 pts for prepping before 2022-02-24 1 pts after.
# prep_score_before = 0 to 15, sum of (0|1) items, where 1 = prepping before Feb 24
# prep_score_after = 0 to 15, sum of (0|1) items, where 1 = prepping eventually (Nov 2022)

```

 These  scores have a convenient conceptualization and a straightforward interpretation
 
 - `Before` - number of preparatory items on the prep list completed before Feb 24
 - `AFter` - number of preparatory steps completed by the hromada at the time of the interview
 - `Total` - the sum of `Before` and `After`. Evaluates the readiness of the hromada at the time of the interview, valuing steps undertaken prior to Feb 24 twice as influential in the final score

`Before` and `After` scores have a more clear conceptualization, but th `Total` score has a more appealing distribution shape, making it more useful for statistical modeling. 

```{r info-score-distribution, fig.height=6, fig.width=4,class.source="fold-hide", cache=T}

g <-  ds1_prep %>%
  # To standardize the metrics of each scale : 0 to 10, where 10 - most prepared
  mutate(
     prep_score = prep_score / 3 # because 15 items, maximum 2 points each
    ,prep_score_before =prep_score_before /1.5 # because 15 items, maximum 1 point each
    ,prep_score_after = prep_score_after /1.5 # because 15 items, maximum 1 point each
  ) %>% 
  select(starts_with("prep_score")) %>% 
  pivot_longer(cols = everything(),names_to = "measure",values_to="value") %>% 
  mutate( 
    measure = factor(measure,
                        levels = c("prep_score_before","prep_score_after","prep_score")
                        ,labels = c("Prep Score (Before)","Prep Score (After)", "Prep Score")
                        )
  ) %>% 
  ggplot(aes(x=value))+
  geom_histogram(binwidth = 1, alpha = .4)+
  scale_x_continuous(breaks = seq(0,10,1))+
  facet_wrap("measure",ncol =1)
g
g %>%  quick_save("score-distribution",w=4, h=6)
```

The item-total correlation also indicates that psychometrically the `Total` score is a better choice - having no negative values and generally having a higher discrimination capacity of items.   

```{r prep-item-total, fig.height=4, fig.width=8,class.source="fold-hide", cache=T}
(d_item_total%>% 
  slice(1:15) %>% 
  pivot_longer(
     cols = c("Total","Before","After")
    ,names_to = "scenario"
    ,values_to = "correlation"
  ) %>% 
  mutate(
    discrimination = case_when(
      correlation <= 0  ~ "problematic"
      ,correlation > 0 & correlation < .2 ~ "poor"
      ,correlation >=.2 & correlation < .4 ~ "good"
      ,correlation >=.4  ~ "very good"
    ) %>% factor(levels = c("problematic","poor","good","very good"))
    ,scenario = scenario %>% factor(level=c("Before","After","Total"))
    ,item_name = factor(item_name, levels = d_meta_prep %>% pull(label_en)) %>% 
      fct_rev()
  ) %>% 
  ggplot(aes(x = item_name, y = correlation, color = discrimination, group = scenario))+
  geom_line(aes(group = "scenario"))+
  geom_point()+
  geom_text(aes(label=correlation %>% scales::number(accuracy = .01) %>% RemoveLeadingZero()),hjust=-.3
            ,size = 3)+
  geom_hline(aes(x=0, yintercept = 0))+ 
  facet_wrap("scenario",nrow=1)+
  scale_y_continuous(limits = c(-.3,.6), expand = expansion(add = c(0,.2)))+
  scale_color_brewer(type ="div",palette = "RdYlGn")+
  coord_flip() +
    labs(
      title = "Item-total corellations under three measurement scenarios"
      ,subtitle = "Before = prior to Feb 24, After = at time of interview, Oct-Nov 2022, Total = Before + After"
      ,y = "Item-total Correlation (Spearman)"
      ,x = NULL
      ,color = "Discrimination"
    )
  ) %>% 
  print() %>% 
  quick_save("item-total",w=8,h=4)
```

While all three metrics should be considered during modeling, our current understanding of the data sugggests that we should prefer the `Total` score in relating hromada's preparedness to other attributes. 

## Prep score change
 
```{r prep-vs-scatter, eval=F}
# Continuous - good for spreading out
comparison_vars_continuous <- c(
   "income_own_per_capita"           
  ,"income_total_per_capita"         
  ,"income_tranfert_per_capita"      
  ,"idp_registration_share"
  ,"idp_real_share"
  ,"idp_child_share"
  
  
  ,"square"
  ,"n_settlements"
  ,"travel_time"
  ,"urban_pct"
  ,"total_population_2022"
  ,"urban_population_2022"                              
  ,"sum_osbb_2020"                                      
  ,"turnout_2020"
  ,"age_head"
  ,"time_before_24th"
)
# Categorical - for color
comparison_vars_discreate <- c(
   "sex_head"
  ,"education_head"
  ,"type"
  ,"voluntary"
  ,"region_en"
)
comparison_vars <- c(
  comparison_vars_discreate
   ,comparison_vars_continuous
)

d <- 
  ds1_prep %>% 
  select(hromada_code, starts_with("prep_score")) %>% 
  left_join(ds0 %>% select(hromada_code,all_of(comparison_vars))) %>% glimpse() %>% 
  mutate(
    across(
      .cols = comparison_vars_discreate
      ,.fns = ~factor(.)
    )
  ) %>%
  pivot_longer(
    cols = comparison_vars_continuous
    ,names_to = "item_name"
    ,values_to = "item_value"
  ) %>% glimpse()

make_plot_prepvs <- function(
    d
    ,xvar    # "prep_score"
    ,yvar    # "item_value"
    ,fillvar # "region_en"
    )
{
  g <- 
  d %>% 
  ggplot(aes(
      x     = !!rlang::sym(xvar)
      ,y    = !!rlang::sym(yvar)
      ,fill = !!rlang::sym(fillvar)
      ))+
  ggplot2::scale_fill_viridis_d(
    begin = 0, end = .8, direction = -1
    ,option = "plasma",guide= guide_legend(reverse=T)
  )+
  facet_wrap(facets = "item_name", scales = "free_y")+
  geom_point(shape=21,color = "black", size =3, alpha = .5, position=position_jitter(seed=42))+
    labs(
      title = paste0("Relationship between Invasion Preparedness Score (horizontal) and other attributes of hromadas")
    )
}  
# To see how it works
d %>% 
  make_plot_prepvs(
    xvar     = "prep_score"
    ,yvar    = "item_value"
    ,fillvar = "region_en"
  )  

# To execution multiple scenarios
for(i in comparison_vars_discreate){
  
  for(ii in c("prep_score","prep_score_before","prep_score_after")){
    g <- 
      d %>% 
      make_plot_prepvs(
        xvar     = ii
        ,yvar    = "item_value"
        ,fillvar = i
      )  %>% 
      file_name <- paste0(ii,"-",i)
    g %>% quick_save(paste0("/1/",file_name),w=12,h=8)
    }
}

```


```{r prep-change-segment-color, eval=F}
# Continuous - good for spreading out
comparison_vars_continuous <- c(
   "income_own_per_capita"           
  ,"income_total_per_capita"         
  ,"income_tranfert_per_capita"      
  ,"idp_registration_share"
  ,"idp_real_share"
  ,"idp_child_share"
  
  
  ,"square"
  ,"n_settlements"
  ,"travel_time"
  ,"urban_pct"
  ,"total_population_2022"
  ,"urban_population_2022"                              
  ,"sum_osbb_2020"                                      
  ,"turnout_2020"
  ,"age_head"
  ,"time_before_24th"
)
# Categorical - for color
comparison_vars_discreate <- c(
   "sex_head"
  ,"education_head"
  ,"type"
  ,"voluntary"
  ,"region_en"
)
comparison_vars <- c(
  comparison_vars_discreate
   ,comparison_vars_continuous
)

d <- 
  ds1_prep %>% 
  select(hromada_code, starts_with("prep_score")) %>% 
  left_join(ds0 %>% select(hromada_code,all_of(comparison_vars))) 

d %>% glimpse()

make_plot_prep_change <- function(
  d
  ,ordervar = "prep_score"
  ,colorvar = "region_en"
){
# browser()
g <- 
  d %>% 
  mutate(
    hromada_code = hromada_code %>% factor() %>% fct_reorder(!!rlang::sym(ordervar))
  ) %>% 
  # sample_n(10) %>% 
  # slice(1:10) %>% 
  ggplot(aes(y=hromada_code, color = !!rlang::sym(colorvar)))+
  geom_segment(
    aes(
      y     = hromada_code
      ,yend = hromada_code
      ,x    = prep_score_before
      ,xend = prep_score_after
      # ,x    = 0                                   # to see only after 
      # ,xend = prep_score_after-prep_score_before  # to see only after
    )
    ,linewidth = 2 ,alpha = .6
  )+
  labs(
    title = paste0("The number of preparedness items secured by hromadas (N= ",
                   d %>% summarize(n=n_distinct(hromada_code)) %>% pull(n)
                   ,") before and after full scale invasion")
    ,subtitle = "Scale guide: (Before) = prior to Feb 24, (After) = at time of interview, Oct-Nov 2022, (Total) = Before + After"
    ,x = "Each segment starts at (Before) score and ends at (After)"
  )+
  # scale_color_viridis_d(
  #   begin = .8, end = .0, direction = -1
  #   , option = "plasma", guide= guide_legend(reverse=T)
  # )+
  scale_color_viridis_c(
    # begin = .8, end = .0, direction = -1
    # , option = "plasma", guide= guide_legend(reverse=T)
  )+
  # scale_color_brewer(type="qual", palette = "Dark2")+
  theme(
    axis.text.y = element_blank()
  )
return(g)
}
(
  d %>% 
  make_plot_prep_change(
    ordervar = "prep_score"
    ,colorvar = "income_own_per_capita"
  )
) %>% 
  quick_save("prep-change-segment-color",w=6,h=9)

```


```{r prep-change-segment-bw, eval=F}
d <- 
  ds1_prep %>% 
  select(hromada_code, starts_with("prep_score")) %>% 
  left_join(ds0 %>% select(hromada_code,all_of(comparison_vars))) 

# d %>% glimpse()

make_plot_prep_change_bw <- function(
    d
  ){
  # browser()
  # level_order <- d %>% arrange(prep_score_after, prep_score_before) %>% pull(hromada_code)
  level_order <- d %>% arrange(prep_score_before, prep_score_after) %>% pull(hromada_code)
  
  g <- 
    d %>% 
    mutate(
      hromada_code = hromada_code %>% factor(levels = level_order)
    ) %>% 
    ggplot(aes(y=hromada_code))+
    geom_segment(
      aes(
        y     = hromada_code
        ,yend = hromada_code
        ,x    = prep_score_before
        ,xend = prep_score_after
        # ,x    = 0                                   # to see only after 
        # ,xend = prep_score_after-prep_score_before  # to see only after
      )
      ,linewidth = 2 ,alpha = .2
    )+
    labs(
      title = paste0("The number of preparedness items secured by hromadas (N= ",
                     d %>% summarize(n=n_distinct(hromada_code)) %>% pull(n)
                     ,")")
      ,subtitle = "(Before) = prior to Feb 24, (After) = at time of interview, Oct-Nov 2022"
      ,x = "Each segment starts at (Before) score and ends at (After)"
      ,caption = "Ordered by Before + After"
      # ,caption = "Ordered by After + Before"
      ,y = NULL
    )+
    theme(
      axis.text.y = element_blank()
      ,panel.grid.major.y = element_blank()
    )
  return(g)
}
(d %>% 
  make_plot_prep_change_bw()
  ) %>% 
   quick_save("prep-change-segment-bw-before",w=5.5,h=9)

```



# Session Information {#session-info}

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Environment </summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
    } else {
      sessionInfo()
    }
```

</details>

```{r session-duration, echo=FALSE}
    report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
