---
title: "EFA: New scale"
output:
  html_document:
    css: ../../libs/css/sidebar.css
    highlight: tango
    keep_md: yes
    theme: flatly
    toc: yes
---
This report narrates the process of factor analizing the proposed scale
<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 12,
  fig.width = 11,
  # out.width = "550px",
  fig.path = 'figures-phase/',     
  dev = "png",
  dpi = 100
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/2-efa/2-efa.R") 
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=FALSE, results='hide', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=FALSE, results='hide', message=FALSE}
```


# Introduction

The purpose of this research was to develop a new scale for measuring subjective wellbing of people condending with substance use disorder using a mobile device. Participants were 427 students of Indiana State University.


# Overview

By comparing various rotations and considering interpretive qualities of the solutions, we have decided to use orthogonal bifactor rotation, as the one that offers the greatest interpretability. 

## Analysis Steps

   
### 1.Scree 
Scree plot is plotted and top eigen values are displayed

### 2.MAP 
`psych::nfactors` call is applied, producing  Very Simple Structure, Velicer's MAP, and other criteria to determine the appropriate number of factors. See [documentation](http://www.personality-project.org/r/html/VSS.html)

### 3.Parallel Analysis 
`psych::fa.parallel` call is applied, comparing the number of factors in the correlation matrix to random "parallel" matrices. For details, see [documentation](https://www.rdocumentation.org/packages/psych/versions/1.6.9/topics/fa.parallel?)

### 4.Fit
`psych::fa` call is applied to conduct maximum likelihood factor analysis (`fm="ml"`) in order to obtain the chi-square of the proposed models, which incrementally increase the number of retained factors. CFI and TLI indices are then computed, following the formulae:
```
  CFI = ((chisq_null-df_null) - (chisq-df))/(chisq_null-df_null)
  TLI = ((chisq_null/df_null) - (chisq/df))/((chisq_null/df_null)-1)
```
For details on `psych::fa` see [documentation](https://www.rdocumentation.org/packages/psych/versions/1.6.9/topics/fa)

### 5.RMSEA 
RMSEA diagnostic is conducted using [Advanced Factor Function](http://statpower.net/Content/312/R%20Stuff/AdvancedFactorFunctions.txt) by James Steiger. The routine relies on the maxim likelihood factor analysis conducted by `stats::factanal` call. For details on the latter see [here](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/factanal.html) 

### 6.Estimate
Using [Advanced Factor Function](http://statpower.net/Content/312/R%20Stuff/AdvancedFactorFunctions.txt) by James Steiger, we conduct maximum likelihood factor analysis, by obtaining the unrotated solution from `stats::factanal` call and then rotating solution using gradient projection algorithms (Bernaards & Jennrich, 2005). 

### 7.Confirm
Applying "Exploratory-Confirmatory" procedure described by [Joreskog(1978)](https://scholar.google.ca/scholar?q=Structural+analysis+of+covariance+and+correlation+matrices&btnG=&hl=en&as_sdt=0%2C33), we find the largest loading for each column of the factor pattern, then constrain all the other loadings in that row to be zero, and fit the resulting model as a confirmatory factor model. Given that we chose the orthogonal bifactor solution, we permit the the cross-loadings between general factor and subfactors. 


# EFA

We create a correlation matrix using all items on the administered scale and conduct eigen diagnostics: 
```{r create-correlation-matrix-0, echo=TRUE, results='hide', message=FALSE}
```
## Scree
```{r diagnose-0a, echo=echoChunks, results='show', message=FALSE, eval=T,fig.width=7, fig.height=5}
```
Scree plot is somewhat ambiguious, suggesting a solution involving up to 3 factors, following the Keiser rule (eigenvalue > 1). 

## MAP
`psych::nfactors` call is applied, producing  Very Simple Structure, Velicer's MAP, and other criteria to determine the appropriate number of factors. See [documentation](http://www.personality-project.org/r/html/VSS.html)

The solution again suggests that no more than 3 meaningful factors can be extracted from the correlation structure.

```{r diagnose-0b, echo=echoChunks, results='show', message=FALSE, eval=T,fig.width=7, fig.height=5}
```

## Parallel
`psych::fa.parallel` call is applied, comparing the number of factors in the correlation matrix to random "parallel" matrices. For details, see [documentation](https://www.rdocumentation.org/packages/psych/versions/1.6.9/topics/fa.parallel?)

There are only two non-general factors that appear to be more distinguishable than their simulated counterparts. While the analysis technically suggests 4 factors, the last one barely makes the cut ( 0.2696 vs 0.2557) and is not supported by the scree test and MAP analysis.  
```{r diagnose-0c, echo=echoChunks, results='show', message=FALSE, eval=T,fig.width=7, fig.height=5}
```

## Fit
`psych::fa` call is applied to conduct maximum likelihood factor analysls (`fm="ml"`) in order to obtain the chi-square of the proposed models, which incrementally increase the number of retained factors. CFI and TLI indices are then computed from the produced criteria. For details on `psych::fa` see [documentation](https://www.rdocumentation.org/packages/psych/versions/1.6.9/topics/fa)
```{r diagnose-0d, echo=echoChunks, results='show', message=FALSE, eval=T,fig.width=7, fig.height=5}
```

## RMSEA
RMSEA diagnostic is conducted using [Advanced Factor Function](http://statpower.net/Content/312/R%20Stuff/AdvancedFactorFunctions.txt) by James Steiger. The routine  relies on the maxim likelihood factor analysis conducted by `stats::factanal` call. For details on the latter see [here](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/factanal.html) 

The confidence intervale of RMSEA point estimate does not include values below the threshhold (<.08) for the models with two factors. When a more liberal threshhold is adopted (<.05), the model with 3 factors appear to be preferable. 
```{r diagnose-0e, echo=echoChunks, results='show', message=FALSE, eval=T,fig.width=7, fig.height=5}
```

## Estimate
Using  [Advanced Factor Function](http://statpower.net/Content/312/R%20Stuff/AdvancedFactorFunctions.txt) by James Steiger, we conduct maximum likelihood factor analysis, by obtaining the unrotated solution from `stats::factanal` call and then rotating solution using gradient projection algorithms (Bernaards & Jennrich, 2005). 

```{r estimate-0, echo=echoChunks, results='show', message=FALSE, warning=F,fig.height = 12,fig.width = 9,out.width="700px"}
```

## Confirm
Applying "Exploratory-Confirmatory" procedure described by [Joreskog(1978)](https://scholar.google.ca/scholar?q=Structural+analysis+of+covariance+and+correlation+matrices&btnG=&hl=en&as_sdt=0%2C33), we find the largest loading for each column of the factor pattern, then constrain all the other loadings in that row to be zero, and fit the resulting model as a confirmatory factor model. Given that we chose the orthogonal bifactor solution, we permit the the cross-loadings between general factor and subfactors. 

```{r confirm-0, echo=echoChunks, results='show', message=FALSE, warning=F,fig.height = 12,fig.width = 7,out.width="700px", eval=T}
```

# Rotations
```{r print-solution, echo=echoChunks, fig.height=10, fig.width=4, message=FALSE, warning=FALSE, results='asis'}
```

# Correlations 

```{r more-cor-1, echo=echoChunks, fig.height=20, fig.width=20, message=FALSE, warning=FALSE, results='asis', out.width = 1200}
```

# Decisions

What items should be included into the daily questionnaire? 

Guidelines for preference:   
- High item-total correlation to the new scale  
- High item-total correlation to the CHU and Warwick scales  
- Items should cover all factors that seem to be present (3)  
- Items with more pronounced weights onto a single factore should be preferred  


1. Even though the new scale shows good unidimentionality, diagnostic tests revealed that there appear to be two subfactors:  
  - "Self-Care"  
    - `Q4_13`(_Today I feel energetic_)  
    - `Q4_5` (_Today I feel rested_)  
    - `Q6_1` (_Today I woke up feeling well-rested_)  
    - `Q6_2` (_Today I ate well_)  
    - `Q6_3` (_Today I took good care of myself_)  

  - "Distress"
    - `Q4_11` (_Today I feel sad_)  
    - `Q4_15` (_Today I feel angry_)  
    - `Q4_4`  (_Today I feel annoyed/irritable_)  
    - `Q4_7`  (_Today I feel in physical pain_)  
    - `Q4_9`  (_Today I feel worried/anxious_)  

2. Item `Q4_4` (_Today I feel annoyed/irritable_) was selected because it consistened loaded the strongest onto the "Distress" factor. 

3. Items `Q4_5`(_Today I feel rested_) and `Q6_1`(_Today I woke up feeling well-rested_) had highest loadings on the "Self-Care" factors, consistently across rotations. Deciding between them, we opted for `Q4_5` because it had slightly higher item-total correlations with both the new and existing scales. These two items had a high correlation (R = .75). 

4. Two other items had the next highest loadings on the "Self-Care" factor: `Q4_13`	(_Today I feel energetic_) and `Q6_3`	(_Today I took good care of myself_). We felt that `Q4_13` was similar to `Q4_5`, whicle `Q6_3` provided a different facet of well-being. Therefore, choosing between the two we settled on the latter.

5. We inclued `Q4_6`	(_Today I feel happy_) because it had the highest loading on the general factor and highest item-total correlation on all scales.  

6. With 4 items included into the new questionnaire, we had 2-3 items to assist `Q4_6` in capturing the genral factor. The following group stood out:
 
  - `Q4_8`   (_Today I feel confident_)
  - `Q4_16`  (_Today I feel in charge of my life_)
  - `Q4_10`  (_Today I feel that my life has a purpose_)
  - `Q4_2`   (_Today I feel optimistic about the future_)

All of these appear to have similar loadings, with minor variations. We chose `Q4_10` because this items appears to cover the spiritual/self-actualization domain. We also chose `Q4_8` it had consistently higher loading on the general factor that other two (`Q4_16` and `Q4_2`) while being similar to them in term of the content. 


7. To represent social facet, we chose `Q4_14` (_Today I feel supported_) over `Q4_3` (_Today I feel loved_), because the former had higher loading, and higher item-total correlations. 

# Chosen items

- `Q4_6`	(_Today I feel happy_) 
- `Q4_8`   (_Today I feel confident_)
- `Q4_10`  (_Today I feel that my life has a purpose_)
- `Q4_14` (_Today I feel supported_)

- `Q6_3` (_Today I took good care of myself_) - SELFCARE subfactor
- `Q4_5`(_Today I feel rested_) - SELFCARE subfactor
- `Q4_4` (_Today I feel annoyed/irritable_)  - DISTRESS subfactor



# Reproducibility
```{r}
sessionInfo()
```
