---
title: "Invasion Prep"
author: 
- "Valentyn Hatsko"
- "Andriy Koval"  
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

> This report visualizes key information about Resilience Survey

___Important Definitions___

> Research Sample: Hromadas who responded to the survey. 

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

```{r set_options, echo=F, message=FALSE, warning=FALSE, results = 'hide'}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/survey-hromada-analysis/survey-1-preparations.R") #This allows knitr to call chunks tagged in the underlying *.R file.
Sys.setlocale("LC_CTYPE", "ukr")
```

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.


<details>
<summary> Packages used <span class="glyphicon glyphicon-plus-sign"></span></summary>
Packages used in current report

```{r load-packages, message=message_chunks, echo=T, results="hide"}
```

</details>
<details>
<summary> External scripts <span class="glyphicon glyphicon-plus-sign"></span></summary>
 
Collection of custom functions used in current repository (`sda-information-requests`)

```{r load-sources, message=message_chunks, echo=T, results="hide"}
```

</details>
  
  
  <details>
  <summary> Global values <span class="glyphicon glyphicon-plus-sign"></span></summary>
  
  
  Values used throughout the report.

```{r declare-globals, message=message_chunks, echo=T, results="hide"}
```

</details>
  
  
  <details>
  <summary> Functions <span class="glyphicon glyphicon-plus-sign"></span></summary>
  
  Custom functions defined for use in this report.

```{r declare-functions, message=message_chunks, echo=T, results="hide"}
```
</details>
  
# Data

## Input
  
```{r load-data, results='show', message=FALSE, cache = T, eval=T}
```

<details>
  <summary> click to glimpse <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r inspect-data, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```
</details>  
> 


Next, we define useful sets of variable names to be used throughout the report

<details>
  <summary> click to see the groups <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r variable-groups, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```
</details> 
>  

<details>
  <summary> meta data <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r meta-data-1,  class.source = "fold-show"}
```
</details> 

  
  
## Transformations 

For the state `ds0`, we augment the focal table of the report with additional columns and transform existing variable to better fit visualization/modeling needs

```{r tweak-data-0, results='show', message=message_chunks,cache=T, class.source = "fold-hide"}
```

To make our analysis more nimble we create four alternative versions of `ds1` with Invasion Preparedness questions

<details>
  <summary> show transformations <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r tweak-data-1,  class.source = "fold-show"}
```
</details> 
> 

<details>
  <summary> examine the versions <span class="glyphicon glyphicon-plus-sign"></span></summary>

```{r inspect-data-1,  class.source = "fold-show"}
```
</details>
  
  
# Variable List 

The following variables are present in the processed data table of survey responses:  
  
```{r results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
ds0 %>% explore::describe_all() %>%neat_DT()
```

# 0. Introduction

<mark>0.1</mark> What is the goal of this report? 
  
> This report explores preparations hromadas were making in anticipation/response to the full-scale invasion  on February 24, 2022

<mark>0.2</mark> How many hromadas contributed responses to so far? 
  
> As of ```r Sys.Date() %>% as.character()```, ```r ds0 %>% summarize(response_count = n_distinct(hromada_code)) %>% pull(response_count) %>% scales::comma()``` hromadas contributed valid response to the survey

# 1. Preparedness Scale

<mark>1.1</mark> What questions were asked about preparations hromadas made? 
  
```{r class.source = "fold-hide"}
ds0 %>% 
  select(preparation) %>% 
  explore::describe_all() %>% 
  left_join(d_meta_prep,by=c("variable"="item_name")) %>% 
  relocate(c("label_ua","label_ua_full"),.after = "variable") %>% 
  select(1:3) %>%
  neat()
```

# Summary of Responses

<mark>1.2</mark> What preparatory steps were most common? 

```{r freq-summary-1, fig.height=5, fig.width=12,class.source="fold-hide",eval=F}
d1 <- 
  ds1_ordinal_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_binary_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(value == "Yes")
  ) %>% 
  left_join(
    d_meta_prep
  ) %>% 
  arrange(item_name, value)

order_of_levels <- 
  d12 %>% 
  left_join(d_meta_prep) %>% 
  filter(value == "Yes") %>% 
  arrange(prop) %>%
  # arrange(desc(item_number)) %>%
  pull(label_en)

g <- 
  d12 %>% 
  mutate(
    display_name = label_en
    ,display_name = factor(display_name, levels = order_of_levels)
    ,value = fct_relevel(
      value
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) 
  ) %>% 
  ggplot(aes(x=prop, y = display_name))+
  geom_point()+
  geom_text(aes(label = str_remove(pct,"\\%")),hjust = -.7, size = 3)+
  geom_segment(aes(x=0,xend=prop,yend=display_name))+
  geom_segment(aes(x=1,xend=1,y=-Inf,yend=Inf),linetype = "dotted", alpha =.5, linewidth = .4, color = "grey50")+
  facet_wrap(facets = "value", nrow=1)+
  scale_x_continuous(breaks = seq(.0,1,.25),labels = scales::percent_format(), expand = expansion(add=c(.05,.15)))+
  labs(
    title = "Have your hromada made the following preparations?"
    ,x = "Percent of respondents", y = NULL
  )+
  theme(
    panel.grid = element_blank()
  )
g
g %>% quick_save("1-preparation-summary",w=12,h=5)

```

```{r freq-summary-2, fig.height=5, fig.width=12,class.source="fold-hide"}
d1 <- 
  ds1_ordinal_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d2 <- 
  ds1_binary_factors %>% 
  pivot_longer(cols = preparation, names_to = "item_name") %>% 
  group_by(item_name,value) %>% 
  summarize(
    count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  group_by(item_name) %>% 
  mutate(
    prop = count/sum(count, rm.na = T)
    ,pct = scales::percent(prop, accuracy = 1)
  ) %>% 
  ungroup()

d12 <- 
  bind_rows(
    d1
    ,d2 %>% filter(value == "Yes")
  ) %>% 
  left_join(
    d_meta_prep
  ) %>% 
  arrange(item_name, value) 

d_in <- 
  d12 %>% 
    mutate(
    display_name = label_en
    ,display_name = factor(
      display_name
      ,levels =  d12 %>%
        left_join(d_meta_prep) %>%
        filter(value == "Yes") %>%
        # filter(value == "Before Feb 24") %>%
        arrange(prop) %>%
        # arrange(desc(item_number)) %>%
        pull(label_en)
    ) # display_name
    ,value = fct_relevel(
      value
      , "Before Feb 24", "After Feb 24","Yes", "No", "Not Applicable",
    ) %>% fct_rev()
  ) %>% select(-label_ua, -label_ua_full)

g <- 
  d_in %>% 
  { 
  ggplot(
    data = (.) %>% filter(value !="Yes") %>% mutate(value=factor(value))
    ,aes(x=prop, y = display_name, fill=value)
  )+
  geom_col(position = position_stack()
           , alpha = .7
           ,data =
  )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = 1
            , size = 4
            ,color="white"
            ,position = position_stack()
            ,data = . %>% filter(value !="Yes")
            )+
  geom_text(aes(label = str_remove(pct,"\\%"))
            ,hjust = -.5
            ,vjust = .5
            , size = 2
            ,color="black"
            ,position = position_stack()
            ,data = (.) %>% filter(value=="Yes") %>% mutate(value=NA)

            )+
  scale_x_continuous(
    breaks = seq(.1,1,.1)
    ,labels = scales::percent_format()
    ,expand = expansion(add=c(-.000,-.0))
  )+
  scale_fill_viridis_d(
    begin = .8, end = .0, direction = -1
    , option = "plasma", guide= guide_legend(reverse=T)
  )+
  labs(
    title = "Have your hromada made the following preparations?"
    ,x = "Percent of respondents", y = NULL, fill = NULL
    ,caption = "Cummulative percent shown in black"
  )+
  theme(
    # panel.grid = element_blank()
    panel.grid.major.y  = element_blank()
    ,panel.border = element_blank()
    ,panel.grid.major.x = element_line(color = "black")
  )
  }

g
g %>% quick_save("2-preparation-summary-yes",w=12,h=5)

```

# Individual Responses

```{r fig.height=3, fig.width=8, message=FALSE, class.source="fold-hide", results='show',results="asis", eval=T, cache =T }

loop_vars <- d_meta_prep %>% pull(item_name) %>% unique()

for(i in seq_along(loop_vars)){
  # i <- 1
  item_name_i <- loop_vars[i]
  item_label <- d_meta_prep %>% filter(item_name==item_name_i) %>% pull(label_ua)
  item_label_full <- d_meta_prep %>% filter(item_name==item_name_i) %>% pull(label_ua_full)
  cat("\n## ", item_name_i,"\n\n")
  cat("\n")
  g <-  ds1_ordinal_factors %>% make_bi_freq_graph(item_name_i)
  g <- 
    g +
    labs(
      title = item_label
      ,subtitle = item_label_full
    )   
  g %>% print()
  cat("\n")
  g <-  ds1_binary_factors %>% make_bi_freq_graph(item_name_i)
  g <- 
    g +
    labs(
      title = item_label
      ,subtitle = item_label_full
    )   
  g %>% print()
  cat("\n")
  # ds1 %>% make_bi_freq_graph("occupation",item_name_i) %>% print()
  # cat("\n")
  # ds1 %>% make_bi_freq_graph(item_name_i,"occupation") %>% print()
  # cat("\n")
  
}
```

# Investigations 

Давайте розглянемо як стать голови ради була пов'язана з заготовкою палива

```{r}
ds1_ordinal_factors %>%
  left_join(ds0 %>% select(hromada_code, sex_head)) %>% 
  make_bi_freq_graph(var1 = "sex_head",var2 = "prep_first_aid_fuel")

ds1_ordinal_factors %>%
  left_join(ds0 %>% select(hromada_code, sex_head)) %>% 
  make_bi_freq_graph(var1 = "prep_first_aid_fuel",var2 = "sex_head")

```



Session Information {#session-info}
===========================================================================
    
For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.
  
  <details>
    <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
    } else {
      sessionInfo()
    }
```
    </details>
      
```{r session-duration, echo=FALSE}
    report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```
    
Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.