---
title: "Agro Survey Overview"
author: 
- "Valentyn Hatsko"
- "Andriy Koval"  
- "Serhii Tytiuk"  
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

> This report visualizes key information about the survey conducted by the Center for Food and Land Use Research (KSE Agrocenter) in June-August 2023

***Important Definitions***

> Research Sample: Hromadas who responded to the survey. In total, 477 hromadas participated in the survey out of 1438 hromadas eligible to take part in the survey

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->

```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

```{r set_options, echo=F, message=FALSE, warning=FALSE, results = 'hide'}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/survey-overview/agro-survey-overview.R") #This allows knitr to call chunks tagged in the underlying *.R file.
# Sys.setlocale("LC_CTYPE", "ukr")
```

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

<details>

<summary>

Packages used

</summary>

Packages used in current report

```{r load-packages, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>

External scripts

</summary>

Collection of custom functions used in current repository (`sda-information-requests`)

```{r load-sources, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>

Global values

</summary>

Values used throughout the report.

```{r declare-globals, message=message_chunks, echo=T, results="hide"}
```

</details>

<details>

<summary>

Functions

</summary>

Custom functions defined for use in this report.

```{r declare-functions, message=message_chunks, echo=T, results="hide"}
```

</details>

# Data

## Input

```{r load-data, results='show', message=FALSE, cache = F, eval=T}
```

<details>

<summary>

click to glimpse

</summary>

```{r inspect-data, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

Next, we define useful sets of variable names to be used throughout the report

<details>

<summary>

click to see the groups

</summary>

```{r variable-groups, results='show', message=message_chunks,cache=F, class.source = "fold-show"}
```

</details>

<details>

<summary>

meta data

</summary>

```{r meta-data-1,  class.source = "fold-show"}
```

</details>

## Transformations

For the state `ds0`, we augment the focal table of the report with additional columns and transform existing variable to better fit visualization/modeling needs

```{r tweak-data-0, results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
```

To make our analysis more nimble we create four alternative versions of `ds1` with Invasion Preparedness questions

<details>

<summary>

show transformations

</summary>

```{r tweak-data-1,  class.source = "fold-show"}
```

</details>

<details>

<summary>

examine the versions

</summary>

```{r inspect-data-1,  class.source = "fold-show"}
```

</details>

# Variable List

The following variables are present in the processed data table of survey responses:

```{r results='show', message=message_chunks,cache=F, class.source = "fold-hide"}
ds0 %>% explore::describe_all() %>%neat_DT()
```

# 0. Introduction

<mark>0.1</mark> What is the goal of this report?

> This report overviews the responses to the survey conducted by \_\_\_\_\_ in Ukraine during 2022

# 1. General Information

<mark>1.1</mark> **How many hromadas contributed responses to so far?**

> As of `r Sys.Date() %>% as.character()`, `r ds0 %>% summarize(response_count = n_distinct(hromada_code)) %>% pull(response_count) %>% scales::comma()` hromadas contributed valid response to the survey

<mark>1.2</mark> **What oblasts are represented in this sample\>?**

```{r class.source="fold-hide"}
ds_survey %>% 
  group_by(region_en, oblast_name_en) %>% 
  summarize(
    hormada_count = n_distinct(hromada_code)
    ,.groups = "drop"
  ) %>% 
  left_join(
    ds_general %>% 
      group_by(region_en=region_en,  oblast_name_en=oblast_name_en) %>% 
      summarize(hromada_count_total = n())
  ) %>% 
  mutate(
    prop = hormada_count/hromada_count_total
    ,pct = scales::percent(prop, accuracy = .1)
  ) %>% 
  arrange(region_en, oblast_name_en) %>% 
  select(-prop) %>% 
  ungroup() %>%
  # neat_DT()
  neat()
```

<mark>1.3</mark> **What type of hromadas are represented in the sample?**

```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("type"))+
  labs(
    title = "What types of hromadas repsonded to the survey?"
    ,subtitle = "Data were collected during June-July of 2022"
    ,y = NULL
  )
```

<mark>1.4</mark> **What hromadas experienced military occupation or military actions?**

```{r fig.height=4, fig.width=8, class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("military_action"))+
  labs(
    title = "How many respondent hromadas have experienced military action at the time of the interview?"
    ,subtitle = "Data were collected during June-July of 2022"
  ) +
  ylab(label = NULL)

(ds0 %>% make_bi_freq_graph("occupation"))+
  labs(
    title = "How many respondent hromadas have experienced occupation at the time of the interview?"
    ,subtitle = "Data were collected during June-July of 2022"
    ,y=NULL
  )

```


<mark>1.5</mark> **Comparison between the survey sample and total population of hromadas based on the list of predictors**

```{r  class.source="fold-hide"}
library(tableone)

predictors_all <- 
  ds_general %>% 
  select(-c("hromada_code", "hromada_name","raion_code", "raion_name","oblast_code",
            "oblast_name","hromada_full_name","hromada_center_code","hromada_center",           
            "lat_center","lon_center", "budget_name", "creation_date", "budget_code", "party", "region_code_en")) %>% 
  colnames()


ds_survey_codes <- 
  ds0 %>% 
  filter(!is.na(hromada_code)) %>% 
  distinct(hromada_code) %>% 
  pull(hromada_code)

ds_surveyed <- 
  ds_general %>% 
  filter(hromada_code %in% ds_survey_codes) %>% 
  mutate(survey_participant = "surveyed" )

ds_comparison <- 
  ds_general  %>% 
  mutate(survey_participant = "all") 

#add to all gromadas (including surveyed) surveyed hromadas one more time to make a comparison
ds_comparison <- rbind(ds_surveyed, ds_comparison) %>% 
  filter(oblast_name_en %ni% c("Luhansk", "Kherson"))

table_pre <- CreateTableOne(vars=predictors_all
                            ,factorVars = c("sex_head", "education_head", "incumbent", "rda")
                            , strata = "survey_participant"
                            , data=ds_comparison)

p <-print(table_pre, smd=T, printToggle = FALSE, noSpaces = TRUE)
knitr::kable(p, format = "html")


```



# 2. Budget

<mark>2.1</mark> What questions were asked about preparations hromadas made?

```{r class.source = "fold-hide"}

ds0 %>%

  ggplot(aes(x = budget_cut_sphere_count)) +

  geom_histogram()

hist(ds0$budget_cut_sphere_count)

```

```{r preparation-summary-1, fig.height=5, fig.width=12,class.source="fold-hide"}

(ds0 %>% make_bi_freq_graph("population_change"))+

  labs(

    title = "How many respondent hromadas have experienced military action at the time of the interview?"

    ,subtitle = "Data were collected during October-November of 2022"

    ,y = NULL

  )

```

<mark>2.2</mark> Whether hromada applied for financial help from state/oblast/raion budget

```{r class.source = "fold-hide"}

(ds0 %>%
  mutate(
    financial_support = factor(financial_support, labels = c("Applied, didn't receive", 
                                                              "Applied, received",
                                                              "Didn't applie, didn't receive",
                                                              "Didn't applie, received"))
    ,financial_support_b = case_when(
      financial_support %in% c("Applied, received", "Didn't applie, received") ~ "Received"
      ,TRUE ~ "Didn't receive"
    )
  ) %>% 
  make_bi_freq_graph("financial_support"))+
  labs(
    title = "Has your hromada applied for and received financial assistance"
    ,subtitle = "Data were collected during June-July of 2022"
    ,y=NULL
  )
```


```{r class.source = "fold-hide"}

ds0 %>%
  mutate(
    financial_support = factor(financial_support, labels = c("Applied, didn't receive", 
                                                              "Applied, received",
                                                              "Didn't applie, didn't receive",
                                                              "Didn't applie, received"))
    ,financial_support_b = case_when(
      financial_support %in% c("Applied, received", "Didn't applie, received") ~ "Received"
      ,TRUE ~ "Didn't receive"
    )
  ) %>% 
  count(party_national_winner, financial_support) %>% 
  group_by(party_national_winner) %>% 
  mutate(pct = n/sum(n)) %>% 
  filter(!is.na(party_national_winner)) %>% 
  ggplot(aes(x = factor(party_national_winner), y = pct, fill = financial_support)) +
  geom_col() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  labs(title = "Applied/received financial assistance by head party affiliation",
       fill = NULL) + 
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) 
```

# 3. Population changes/IDPs

<mark>3.1</mark> **How hromadas population has changed since February 24th**

```{r population-change-1, fig.height=5, fig.width=12,class.source="fold-hide"}
(ds0 %>% make_bi_freq_graph("population_change"))+
  labs(
    title = "Changes in popultion since February 24th"
    ,subtitle = "Data were collected during October-November of 2022"
    ,y = NULL
  )
```

```{r , fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>%
  count(population_change, idp_pct) %>% 
  group_by(population_change) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = population_change, y = pct, fill = idp_pct)) +
  geom_col() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  labs(title = "Applied/received financial assistance by head party affiliation",
       fill = NULL) + 
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) 

```


<mark>3.2</mark> **Share of IDPs among total population by region**

```{r population-change-2, fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  count(region_en, idp_pct) %>% 
  group_by(region_en) %>% 
  mutate(pct = n/sum(n)) %>% 
  mutate(idp_pct = factor(idp_pct, levels = c(
    "Не прибували, кількість населення в громаді зменшилася"
    ,"До 5% від населення громади"
    ,"5-10% від населення громади"
    ,"11-20% від населення громади"
    ,"Понад 20% від населення громади"
  ))) %>% 
  ggplot(aes(x = region_en, y = pct, fill = idp_pct)) +
  geom_col() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  labs(title = "% of IDPs",
       fill = NULL) + 
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  scale_fill_brewer(palette="PuBu")

```

<mark>3.4</mark> **Relation between number of passengers in 2021 and number of IDps**

#TO_DO: check passengers numbers \# `{r population-change-passangers, fig.height=5, fig.width=12,class.source="fold-hide"} # ds0 %>%  #   filter(passangers_2021 < 500000) %>%  #   ggplot(aes(x = passangers_2021, y = idp_number)) + #   geom_point() + #   geom_smooth(method = "lm", se=F) + #   theme_bw()   #`

<mark>3.4</mark> **Modelling of relation between number of IDPs and predictors**

```{r population-change-models, results= "asis", class.source="fold-hide"}


```

# 4. Situation with services

<mark>4.1</mark> **How much time provision of all admin services were suspended**

```{r services-admin, fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  count(admin_services_stopped, admin_services_resumed) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = admin_services_stopped , y = pct, fill = admin_services_resumed)) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension and resumption of services') +
  xlab("Services stopped") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Status of service resumption"
                   ,values = c("#093058", "#EC4544", "#1DB5C4", "grey"))
```


```{r fig.height=5,fig.show="hold", out.width="50%, fig.width=12,class.source="fold-hide"}
# par(mar = c(4, 4, .1, .1))

ds0 %>% 
  group_by(military_action) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = military_action , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per military actions status') +
  xlab("Military actions status") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether provision of services was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))

```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(region_en) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = region_en , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per region') +
  xlab("Region") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether provision of services was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))
```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(type) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = type , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per hromada type') +
  xlab("Type") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether provision of services was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))
```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(region_en, type) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = region_en , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  facet_wrap(~ type) +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per region and hromada type') +
  xlab("Region") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether provision of \nservices was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))
```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(region_en, type) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = region_en , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  facet_wrap(~ type) +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per region and hromada type') +
  xlab("Region") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether provision of \nservices was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))
```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(no_party) %>% 
  count(admin_services_stopped) %>% 
  mutate(pct = n/sum(n)) %>% 
  na.omit() %>% 
  ggplot(aes(x = as.factor(no_party) , y = pct, fill = factor(admin_services_stopped))) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of services per party affiliation of the head') +
  xlab("No party status") +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = c("Represent some party", "No party")) +
  scale_fill_manual(name = "Whether provision of \nservices was stopped"
                    ,labels =c("No", "Yes")
                   ,values = c("#1DB5C4", "#EC4544"))
```


<mark>4.2</mark> **Interruption of garbage collection**

```{r services-garbage, fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  count(garbage_interruptions, garbage_functional) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = garbage_interruptions , y = pct, fill = garbage_functional)) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  xlab("Hromada had interruption with garbage collection") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Current status of garbage collection"
                   ,values = c("#EC4544", "#1DB5C4"))
```

```{r fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  group_by(military_action) %>% 
  count(garbage_interruptions) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = military_action , y = pct, fill = factor(garbage_interruptions))) +
  geom_col() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Suspension of garbage collection per military actions status') +
  xlab("Military actions status") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(name = "Whether garbage collection was stopped"
                    ,labels =c("Hard to say", "No", "Yes")
                   ,values = c("grey90", "#1DB5C4", "#EC4544"))
```


<mark>4.3</mark> **Modeling of relation between suspension time of admin services and different predictors**

```{r services-models, results="asis", class.source="fold-hide"}


```

<mark>4.4</mark> **Modeling of relation between garbage collection interruptions and different predictors**

```{r garbage-models, results="asis", class.source="fold-hide"}

```

# 5. Volunteers/humanitarian hubs

<mark>5.1</mark> **Relation between number of hubs and total population**

```{r hubs, fig.height=5, fig.width=12,class.source="fold-hide"}
#TO CHANGE
d_volunteers %>% 
  ggplot(aes(x = total_population_2022, y = humanitarian_hubs)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between volunteers per capita and humanitarian hubs') +
  xlab("% of volunteers out of total population")

```

<mark>5.2</mark> **Relation between % of volunteers and number of hubs**

```{r, fig.height=5, fig.width=12,class.source="fold-hide"}
d_volunteers %>% 
  ggplot(aes(x = volunteers_per_capita, y = humanitarian_hubs)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between volunteers per capita and humanitarian hubs') +
  xlab("% of volunteers out of total population")

```

<mark>5.3</mark> **Relation between % of volunteers and total population**

```{r results = "asis", class.source="fold-hide"}
#TO CHANGE
d_volunteers %>% 
  filter(total_population_2022 <200000) %>% 
  ggplot(aes(x = log(total_population_2022) , y = volunteers_number, color = type)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  theme_bw() +
  labs(title = 'Relation between volunteers per capita and humanitarian hubs') +
  xlab("% of volunteers out of total population")

```

# 6. Aid providers

<mark>6.1</mark> **Share of hromadas in each region which received aid from other countries**

```{r countries-regions, fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  count(region_en, foreign_aid) %>% 
  group_by(region_en) %>% 
  mutate(pct = n/sum(n)) %>% 
  ggplot(aes(x = region_en, y = pct, fill = foreign_aid)) +
  geom_col() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  labs(title = 'Aid from other countries per regions')
```

<mark>6.2</mark> **Relation between number of countries as aid providers and number of international organizations**

```{r countries-ingos, fig.height=5, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  ggplot(aes(x = ingo_count, y = countries_count)) +
  geom_jitter() +
  geom_smooth(method = "lm", se=F) +
  theme_bw()

```

<mark>6.3</mark> **Average number of countries and INGOs provided aid by region and type**

```{r countries-ingos-2, fig.height=12, fig.width=12,class.source="fold-hide"}

ds0 %>% 
  select(hromada_name, region_en, type, countries_australia:countries_japan) %>% 
  pivot_longer(-c(hromada_name, region_en, type), names_to = "country", values_to = "received") %>% 
  mutate(
    received = replace(received, is.na(received), 0)
  ) %>% 
  group_by(hromada_name, region_en) %>% 
  mutate(n = sum(received)) %>% 
  ungroup() %>% 
  distinct(hromada_name, region_en, type, n) %>% 
  group_by(region_en, type)  %>% 
  summarise(mean = mean(n), .groups = "drop", var = "country") %>% 
  rbind(
    ds0 %>% 
      select(hromada_name, region_en, type, starts_with("ingo_"), -ingo_other, -ingo_other_text, -ingo_count) %>% 
      pivot_longer(-c(hromada_name, region_en, type), names_to = "ingo", values_to = "received") %>% 
      group_by(hromada_name, region_en) %>% 
      mutate(n = sum(received)) %>% 
      ungroup() %>% 
      distinct(hromada_name, region_en, type, n) %>% 
      group_by(region_en, type)  %>% 
      summarise(mean = mean(n), .groups = "drop", var = "ingo") 
  ) %>% 
  ggplot(aes(x = var, y = mean, fill = var)) +
  geom_bar(stat = "identity") +
  facet_wrap(~region_en + type, ncol = 3) +
  geom_text(aes(label=round(mean, digits = 2)), vjust = -0.2, color="black", size=3.5) +
  ylim(0, 4.5)

```


<mark>6.3</mark> **How many hromadas covered by aid from each country ?**

```{r countries-rating, fig.height=12, fig.width=12,class.source="fold-hide"}
ds0 %>% 
  filter(foreign_aid == "Так") %>% 
  select(hromada_name, region_en, countries_australia:countries_japan) %>% 
  pivot_longer(-c(hromada_name, region_en), names_to = "country", values_to = "received") %>% 
  mutate(
    country = str_to_title(str_remove(country, "countries_"))
  ) %>% 
  group_by(country) %>% 
  summarise(n = sum(received), .groups = "drop") %>% 
  filter(n>0)  %>% 
  ggplot(aes(x = n, y = fct_reorder(country, n))) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label=n), hjust = -0.2, color="black", size=3.5) +
  theme(axis.text.y = element_text(size = 11),
        axis.title.y = element_blank()) 
```


<mark>6.4</mark> **How many hromadas covered by aid from each aid provider?**

```{r ingos-rating, fig.height=12, fig.width=12,class.source="fold-hide"}

ds0 %>% 
  select(hromada_name, region_en, starts_with("ingo_"), -ingo_other, -ingo_other_text, -ingo_count) %>% 
  pivot_longer(-c(hromada_name, region_en), names_to = "ingo", values_to = "received") %>% 
  mutate(
    ingo = str_to_upper(str_remove(ingo, "ingo_"))
  ) %>% 
  group_by(ingo) %>% 
  summarise(n = sum(received), .groups = "drop") %>% 
  filter(n>1)  %>% 
  ggplot(aes(x = n, y = fct_reorder(ingo, n))) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label=n), hjust = -0.2, color="black", size=3.5) +
  theme(axis.text.y = element_text(size = 11),
        axis.title.y = element_blank()) 
```


<mark>6.5</mark> **Relation between population and number of organizations**

```{r models-countries, results = "asis", class.source="fold-hide"}
ds0 %>% 
  ggplot(aes(x = log(total_population_2022), y= ingo_count)) +
  geom_point() + 
  geom_smooth(method = "lm")
  theme(axis.text.y = element_text(size = 11),
        axis.title.y = element_blank())   

```

<mark>6.6</mark> **Relation between population and number of organizations**
```{r models-countries, results = "asis", class.source="fold-hide"}
ds0 %>% 
  ggplot(aes(x = log(total_population_2022), y= ingo_count)) +
  geom_point() + 
  geom_smooth(method = "lm")
  theme(axis.text.y = element_text(size = 11),
        axis.title.y = element_blank())   

```



<mark>6.6</mark> **Modelling of relation between number of aid providers and different predictors**

```{r models-aid-providers, results = "asis", class.source="fold-hide"}
  

```

# 7. Aid received

<mark>7.1</mark> **Modelling of relation between volume of received aid and different predictors**

```{r aid received, results = "asis", echo=FALSE, warning = FALSE, class.source="fold-hide"}



```

# 8. Relocation and new projects

<mark>8.1</mark> **Modelling of relation between relocated enterprises and different predictors**

```{r relocated, results = "asis", echo=FALSE, warning = FALSE, class.source="fold-hide"}



```

# Session Information {#session-info}

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>

Environment

</summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
    } else {
      sessionInfo()
    }
```

</details>

```{r session-duration, echo=FALSE}
    report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
